---
title: "Predicting Type of Exercise Using Data From Wearable Devices"
author: "Warren"
date: "07/05/2020"
output: html_document
params: 
    new_title: "index"
title: "`r params$index`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

## Preprocessing
#### Downloading Training and Test Datasets
```{r}
fileURL1<- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
fileURL2<- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

download.file(fileURL1, destfile="./train.csv", method="curl")
download.file(fileURL2, destfile="./test.csv", method="curl")

dateDownloaded<-date()
```

#### Reading and Cleaning Training Data
```{r}
train<-read.csv("train.csv", na.strings=c("NA","","#DIV/0!"))
train<-train[,colSums(is.na(train)) == 0]
```

#### Read and cleaning Testing Data into R
```{r}
test<-read.csv("test.csv", na.strings=c("NA","","#DIV/0!"))
test<-test[,colSums(is.na(test)) == 0]
```

#### Explore

```{r results='hide'}
str(train)
str(test)
```

#### Loading packages
```{r}
library(caret)
library(randomForest)
library(e1071)
library(dplyr)
```

#### Set seed
```{r}
set.seed(123456)
```

## Remove variables that do not predict type of exercise
```{r}
train<-train[,-c(1:7)]
test<-test[,-c(1:7)]
```

## Building Prediction Algorithm and Evaluation
#### Partition Data
```{r}
inTrain     <- createDataPartition(train$classe, p = 0.6, list = FALSE)
training  <- train[inTrain,]
testing    <- train[-inTrain,]
```

#### Making random forest
```{r cache=TRUE}
modFit<- randomForest(classe~., data=training, prox=TRUE)
modFit
```

#### Cross validation
```{r message=FALSE, cache=TRUE}
library(rfUtilities)
rf.crossValidation(modFit, training[,1:52], p=0.6, n=4, ntree=500)
```


## Predicting Exercise Type Using Test Data Subsetted from Training Data
```{r}
predTest<-predict(modFit, newdata=testing)
```

## Evaluating model
```{r}
confusionMatrix(predTest, testing$classe)
```

The out of sample error rate is 0.0062 04 0.62%

## Using Model for Quiz
```{r}
print(predict(modFit, newdata=test))
```